Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-02-15 RNARedPrint-Bioinfo2018.tex
Added PKs cosmetically

\abstract{\textbf{Motivation:} The design of multi-stable RNA molecules has important applications in biology, medicine, and biotechnology. Synthetic design approaches largely benefit from effective in-silico methods, which can tremendously impact their cost and feasibility. \\
\textbf{Results:} Here, we revisit a central ingredient of most in-silico design methods: the sampling of sequences for multi-target design. We establish the $\#${\sf P}-hardness of uniform sampling, and introduce \ourprog{}, a tree decomposition-based algorithm for efficient, fixed parameter tractable sampling. By modeling the problem as a constraint network, \ourprog{} supports generic Boltzmann-weighted sampling for arbitrary additive RNA energy models; this enables generating designs meeting specific goals like expected free energies or \GCb-content. Finally, we empirically study general properties of the approach and generate biologically relevant multi-target Boltzmann-weighted designs for a common design benchmark. In particular, we show significant improvements over seed sequences generated by uniform sampling, the previously best available sampling strategy for multi-target design.\\
\textbf{Availability:} Our software is freely available at: \url{https://github.com/yannponty/RNARedPrint}\\
\textbf{Contact:} \href{yann.ponty@lix.polytechnique.fr}{yann.ponty@lix.polytechnique.fr}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
online.}

>>>>

\abstract{\textbf{Motivation:} The design of multi-stable RNA molecules has important applications in biology, medicine, and biotechnology. Synthetic design approaches largely benefit from effective in-silico methods, which can tremendously impact their cost and feasibility. \\
\textbf{Results:} Here, we revisit a central ingredient of most in-silico design methods: the sampling of sequences for the design of multi-target structures, possibly including pseudoknots. We establish the $\#${\sf P}-hardness of uniform sampling, and introduce \ourprog{}, a tree decomposition-based algorithm for efficient, fixed parameter tractable sampling. By modeling the problem as a constraint network, \ourprog{} supports generic Boltzmann-weighted sampling for arbitrary additive RNA energy models; this enables the generation of RNA sequences meeting specific goals like expected free energies or \GCb-content. Finally, we empirically study general properties of the approach and generate biologically relevant multi-target Boltzmann-weighted designs for a common design benchmark. Our results show significant improvements over seed sequences generated by uniform sampling, the previously best available sampling strategy for multi-target design.\\
\textbf{Availability:} Our software is freely available at: \url{https://github.com/yannponty/RNARedPrint}\\
\textbf{Contact:} \href{yann.ponty@lix.polytechnique.fr}{yann.ponty@lix.polytechnique.fr}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
online.}
